---
title: "Linear regressions for niche analysis of Acaena clades"
author: "Miki Nomura"
date: "27 February 2018"
output:
  pdf_document: default
  word_document: default
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(knitr)

# Root directory for rmd files is the folders where the files are in. 
opts_knit$set(root.dir='../')
```

```{r Data preparation, include=FALSE}

genus_name <- "Acaena"
# genus_name <- "Chionochloa"

source(".//Chionochloa niche evolution//00_DataPreparation.R")

ageVolData <- read.csv(paste("NicheVolume_age_", genus_tag, ".csv", sep = ""))
overlapPdData <- read.csv(paste("Nicheovrlap_PD_", genus_tag, ".csv", sep = ""))

```

## Sister species pairs' Phylogenetic distances ~ niche overlap of occurrence records
Niche overlap ranges 0 - 1, so I delimited y axis but it got rid of confidense interval from this figure.
```{r Phylogenetic distance - nihce overlap}

sisOverlapPd <- (overlapPdData$node1 %in% sispairs[,1]) %>% overlapPdData[., ]

myplot <- plotAnalysis(data = sisOverlapPd, 
                       yv = "nicheOverlap", xv = "phyloDistance", 
                       nodeNumbercol = "node1", showStats = T,
                       ylabname = "Niche overlap of occurrence records", 
                       xlabname = "Phylogenetic distances between sister species pairs",
                       label.point = TRUE
) +
  ylim(0, 1)


plot(myplot)

rm(myplot)

```

## Sister species pair - their ancestor's sister node
## Phylogenetic distances ~ niche overlap of occurrence records

```{r Sister species pair and their aunt clade}

ancSisNode <- sapply(sispairs[,1], function(i){
  
  ancestor <- tree$edge[which(i == tree$edge[, 2])]
  ancestorSisNode <- distance2[distance2[,"node"] == ancestor, "sisterNode"]
  return(ancestorSisNode)
  
}
)

ancsisOverlapPd <- rbind(
  ((overlapPdData$node1 %in% ancSisNode) %>% overlapPdData[., ]),
  ((overlapPdData$node2 %in% ancSisNode) %>% overlapPdData[., ])
)

dup <- duplicated(ancsisOverlapPd$nicheOverlap) %>% which
ancsisOverlapPd <- ancsisOverlapPd[-dup, ]

myplot <- plotAnalysis(data = ancsisOverlapPd,
                       yv = "nicheOverlap", xv = "phyloDistance", 
                       nodeNumbercol = "node1", showStats = T,
                       ylabname = "Niche overlap of occurrence records", 
                       xlabname = "Phylogenetic distances between sister species pair and its closest clade",
                       label.point = TRUE
) +
  ylim(0, 1)


plot(myplot)

rm(myplot)

```


## Clade Phylogenetic distances ~ niche overlap of occurrence records
```{r}
### Omit duplicated pairs
dup <- duplicated(overlapPdData$phyloDistance) %>% which
overlapPdData <- overlapPdData[-dup, ]


### Eliminate sister species pairs
overlapPdclade <- (!(overlapPdData$node1 %in% sispairs[ , 1])) %>% overlapPdData[.,]


### Eliminate outlier of clade age

outlier <- which(max(overlapPdclade$phyloDistance) == overlapPdclade$phyloDistance)

overlapPd <- overlapPdclade[-outlier, ]

myplot <- plotAnalysis(data = overlapPd,
                       yv = "nicheOverlap", xv = "phyloDistance", 
                       nodeNumbercol = "node1", showStats = T,
                       ylabname = "Niche overlap of occurrence records",
                       xlabname = "Phylogenetic distances between clades",
                       label.point = TRUE
) +
  ylim(0, 1)

plot(myplot)

rm(myplot)
```

## Clade ages ~ niche volume of occurrence records

```{r}

### Eliminate outlier
outlier <- which(max(ageVolData$speciesAge) == ageVolData$speciesAge)

myplot <- plotAnalysis(data = ageVolData[-outlier,],
                       yv = "nicheVolume", xv = "speciesAge", 
                       nodeNumber = "node1", showStats = T,
                       ylabname = "Niche volume of occurrence records",
                       xlabname = "Clade age",
                       label.point = TRUE
) +
  ylim(0, 1)

plot(myplot)

rm(myplot)


### Leave outlier
myplot <- plotAnalysis(data = ageVolData,
                       yv = "nicheVolume", xv = "speciesAge", 
                       nodeNumber = "node1", showStats = T,
                       ylabname = "Niche volume of occurrence records",
                       xlabname = "Clade age",
                       label.point = TRUE
) +
  ylim(0, 1)

plot(myplot)
rm(myplot)
```

