---
title: "Linear regressions for niche analysis of Acaena clades"
author: "Miki Nomura"
date: "21 March 2018"
output:
  pdf_document: default
  word_document: default
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(knitr)

# Root directory for rmd files is the folders where the files are in. 
opts_knit$set(root.dir='../')
```

```{r Data preparation, include=FALSE}

#genus_name <- "Acaena"
genus_name <- "Chionochloa"

source(".//Chionochloa niche evolution//00_DataPreparation.R")

# Species age - niche volume
ageVolData <- read.csv(paste("NicheVolume_age_", genus_tag, ".csv", sep = ""))
# Time since divergence - niche overlap
overlapPdData <- read.csv(paste("Nicheovrlap_PD_", genus_tag, ".csv", sep = ""))
# Proportion of secondary open habitat
secondaryOpen <- read.csv(paste("Y://", genus_name, "_data_analyses.csv", sep = ""))

```

## Fig. 1 Sister species pairs' divergence time ~ niche overlap of occurrence records
Numbers above points are node ID of one of sister species

```{r Phylogenetic distance - nihce overlap}

sisOverlapPd <- (overlapPdData$node1 %in% sispairs[,1]) %>% overlapPdData[., ]

### Eliminate outlier
outlier <- which(max(sisOverlapPd$divergenceTime) == sisOverlapPd$divergenceTime)

myplot <- plotAnalysis(data = sisOverlapPd, genus_name = genus_name,
                       yv = "nicheOverlap", xv = "divergenceTime", 
                       nodeNumbercol = "node1", showStats = T,
                       ylabname = "Niche overlap of occurrence records", 
                       xlabname = "Time since divergence",
                       label.point = TRUE
) +
  ylim(0, 1) # Niche overlap ranges 0 - 1, so I delimited y axis but it can get rid of confidense interval from this figure.


plot(myplot)

rm(myplot)

```


## Fig. 2 Sister species pair - their ancestor's sister node
## Divergence time ~ niche overlap of occurrence records
Numbers above points are node ID of ancestor's sister

```{r Sister species pair and their aunt clade}

# Get ancestor's sister node (aunt for sister species pairs)
ancSisNode <- sapply(1:nrow(sispairs), function(i){
  
  ancestor <- tree$edge[which(sispairs[i, 1] == tree$edge[, 2])]
  ancestorSisNode <- distance2[distance2[,"node"] == ancestor, "sisterNode"]
  
  nodelist <- cbind(sispairs[i, ], ancestor, ancestorSisNode)
  return(nodelist)
  
}
)

ancSisNode <- data.frame(t(ancSisNode))

ancsisOverlapPd <- rbind(
  ((overlapPdData$node1 %in% ancSisNode$ancestorSisNode) %>% overlapPdData[., ]),
  ((overlapPdData$node2 %in% ancSisNode$ancestorSisNode) %>% overlapPdData[., ])
)

targetover <- list()
for(i in 1:nrow(sispairs)){
  node <- (overlapPdData$node1 == ancSisNode$ancestorSisNode[i]) %>% which
if(overlapPdData$node2[node] == ancSisNode$ancestor[i]){
  target <- overlapPdData[node, ]
  targetover[[i]] <- cbind(target, ancSisNode[i,])
}
}


ancsisOverlapPd <- do.call(rbind, targetover)

myplot <- plotAnalysis(data = ancsisOverlapPd, genus_name = genus_name,
                       yv = "nicheOverlap", xv = "divergenceTime", 
                       nodeNumbercol = "node1", showStats = T,
                       ylabname = "Niche overlap of occurrence records", 
                       xlabname = "Time since divergence of parent node of sister species pair and its closest clade",
                       label.point = TRUE
) +
  ylim(0, 1)


plot(myplot)

rm(myplot)

```

## Fig. 3 Species age ~ niche volume of occurrence records
Numbers above points are node ID of one of sister species

```{r}

### Extract sepcies
clade <- is.na(ageVolData$spname) %>% which
### Eliminate outlier
outlier <- which(max(ageVolData$speciesAge[-clade]) == ageVolData$speciesAge)

myplot <- plotAnalysis(data = #ageVolData[-c(outlier, clade), ], 
                         ageVolData[-clade, ],
                       genus_name = genus_name,
                       yv = "nicheVolume", xv = "speciesAge",
                       nodeNumbercol = "node1", showStats = T,
                       ylabname = "Niche volume of occurrence records",
                       xlabname = "Species age",
                       label.point = TRUE
) +
  ylim(0, 1)

plot(myplot)

rm(myplot)

```

##  Fig. 4 Clade divergence time ~ niche overlap of occurrence records
Numbers above points are node ID of one of sister clades

```{r}

### Omit duplicated pairs
dup <- duplicated(overlapPdData$divergenceTime) %>% which
overlapPdData2 <- overlapPdData[-dup, ]


### Eliminate sister species pairs
overlapPdclade <- (!(overlapPdData2$node1 %in% sispairs[ , 1])) %>% overlapPdData2[.,]


# ### Eliminate outlier of clade age
# outlier <- which(max(overlapPdclade$divergenceTime) == overlapPdclade$divergenceTime)
# overlapPd <- overlapPdclade[-outlier, ]

myplot <- plotAnalysis(data = overlapPdclade, genus_name = genus_name,
                       yv = "nicheOverlap", xv = "divergenceTime", 
                       nodeNumbercol = "node1", showStats = T,
                       ylabname = "Niche overlap of occurrence records",
                       xlabname = "Time since divergence of sister clades",
                       label.point = TRUE
) +
  ylim(0, 1)


plot(myplot)

rm(myplot)
```

##  Fig. 5 Clade ages ~ niche volume of occurrence records
Numbers above points are node ID of clade. One outlier of clade age was omitted.

```{r}

### Extract sepcies
clade <- is.na(ageVolData$spname) %>% which
sp <- (1:nrow(ageVolData))[-clade]
### Eliminate outlier
# outlier <- which(max(ageVolData$speciesAge) == ageVolData$speciesAge)

myplot <- plotAnalysis(data = ageVolData[-sp,], genus_name = genus_name,
                       yv = "nicheVolume", xv = "speciesAge", 
                       nodeNumbercol = "node1", showStats = T,
                       ylabname = "Niche volume of occurrence records",
                       xlabname = "Clade age",
                       label.point = TRUE
) +
  ylim(0, 1)

plot(myplot)

rm(myplot)


```



##  Fig. 6 Proportion of secondary open habitat ~ Species ages

```{r}

ageSecondary <-  merge(ageVolData, secondaryOpen, by.x = "spname", by.y = "spname")

myplot <- plotAnalysis(data = ageSecondary, genus_name = genus_name,
                       yv = "proportionSecondaryHabitat", xv = "speciesAge", 
                       nodeNumbercol = NULL, showStats = T,
                       ylabname = "Proportion of secondary open habitat",
                       xlabname = "Species age",
                       label.point = FALSE
) +
  ylim(0, 1)

plot(myplot)

rm(myplot)


```

